Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-11-13 papers/SiVL2018/sivl_2018_6pages.tex

In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming. We focus on collections  that have been used for object recognition, referring expression generation, phrase localization in previous work, but do not discuss other collections for e.g. image captioning which typically do not link mentions of objects to corresponding image regions.

@@

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories. ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.

@@

\paragraph{Analysis} We parse REs in RefCocowith the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.
We estimate this distance as the minimal path length of all synsets of a word  to the root node.
Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the RefCoco data set.
We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
At the same time, this overview clearly suggests that object names in RefCoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).

@@

By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
in contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
On the other hand, \flickr is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
		\item[(2)] \textbf{Exhaustive annotations}: are not available
		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)

@@

\subsection{Object detectors}
As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.

@@

In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
The comparison between different data sets and available annotations for them reveals that consist procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to use of concepts) turns out to be difficult.

>>>>

In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming. We focus on collections  that have been used for object recognition, referring expression generation, and phrase localization in previous work, but do not discuss other collections for e.g. image captioning which typically do not link mentions of objects to corresponding image regions.

@@

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories (e.g.,~the ILSVRC image classification challenge comprises 1k synsets \cite{ILSVRC15}). 
ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.

@@

\paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
We estimate this distance as the minimal path length of all synsets of a word  to the root node.
Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).

@@

By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
in contrast to \refcoco/+, the production of entity mentions did not underlie any constraints. 
On the other hand, it is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.

\begin{itemize}
     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
		\item[(2)] \textbf{Exhaustive annotations}: are not available
		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in REs; e.g.,~both animals in the right-most image in Fig.~\ref{fig:graf_genome} are named \refexp{dog})

@@

\subsection{Object detectors}
In order to obtain a sufficiently specific level for all objects in an image, an alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.

@@

In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
The comparison between different data sets and available annotations for them reveals that consistent procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to the use of concepts) turns out to be difficult.
